\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-18 src/tex/ms.tex
Updates throughout

The Fisher information matrix for a single detector is typically given by 
\begin{equation}
    F^{k}_{ij} = (\partial_i h_0 | \partial_j h_0) \, ,
\end{equation}
where $k$ indicates the detector, $\partial_i = \partial/\partial \theta_i$, and $h_0$ is the strain measured by the detector which is given by,
\begin{equation}
    h_0(\theta) = F_+(\lambda) h_{+}(\phi) + F_\times(\lambda) h_{\times}(\phi) \, .
\end{equation}
Here we have separated out the intrinsic ($\phi$) and extrinsic ($\lambda$) variables.
Since we are considering a three detector setup we simply add the Fisher matrices from the individual detectors to get the combined Fisher matrix:
\begin{equation}
    F_{ij} =  F^{\mathrm{Hanford}}_{ij} + F^{\mathrm{Livingston}}_{ij} + F^{\mathrm{Virgo}}_{ij}   \, .
\end{equation}
Finally, we invert the Fisher matrix to calculate the covariance matrix.

To illustrate the computational speed of computing Fisher matrices with AD, we consider a population of binaries and compute the sky localtization error following Eq.~(28) in \citep{Iacovelli:2022bbs, Iacovelli:2022mbg}.
Since the Fisher matrix approach is known to have both theoretical issues as well as numerical instabilities for low signal-to-noise events, we restrict our population to only nearby systems.
A full list of the distributions used to generate the various parameters in our population are given in Tab...

The distribution of sky localization errors from a a population of $10^3$ binaries can be seen in Fig... 
We have verified that our errors agree with a separate dedicated Fisher forecasting code~\citep{Borhanian:2020ypi} to within X percent.
This demonstrates that AD can be used to accurately produce population level forecasts.

>>>>

The Fisher information matrix for a single detector is typically given by 
\begin{equation}
    \mathcal{I}^{k}_{ij} = (\partial_i h_0 | \partial_j h_0) \, ,
\end{equation}
where $k$ indicates the detector, $\partial_i = \partial/\partial \theta_i$, and $h_0$ is the strain measured by the detector which is given by,
\begin{equation}
    h_0(\theta) = F_+(\lambda) h_{+}(\phi) + F_\times(\lambda) h_{\times}(\phi) \, .
\end{equation}
Note that here we have separated out the intrinsic ($\phi$) and extrinsic ($\lambda$) variables as well as introducing the detector projection functions for the plus and cross polarizations as $F_+$ and $F_\times$ respectively.
Since we are considering a three detector setup we simply add the Fisher matrices from the individual detectors to get the combined Fisher matrix:
\begin{equation}
    \mathcal{I}_{ij} =  \mathcal{I}^{\mathrm{Hanford}}_{ij} + \mathcal{I}^{\mathrm{Livingston}}_{ij} + \mathcal{I}^{\mathrm{Virgo}}_{ij}   \, .
\end{equation}
Finally, we invert the Fisher matrix to calculate the covariance matrix.

To illustrate the computational speed of computing Fisher matrices with AD, we consider a population of binaries and compute the sky localtization error following Eq.~(28) in \citep{Iacovelli:2022bbs, Iacovelli:2022mbg}.
Since the Fisher matrix approach is known to have both theoretical issues as well as numerical instabilities for low signal-to-noise events, we restrict our population to only nearby systems.
A full list of the distributions used to generate the various parameters in our population are given in Tab...
The resulting population produces binaries with signal-to-noise ratios ranging from $\mathcal{O}(10-10^2)$.

\begin{figure}[ht!]
    \script{sky_localization.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/sky_localization.pdf}
        \caption{
            This plot should show a sky localization error bar.
        }
        \label{fig:sky_localization}
    \end{centering}
\end{figure}

The distribution of sky localization errors from a a population of $10^3$ binaries can be seen in Fig.~\ref{fig:sky_localization}.
We have verified that our errors agree with a separate dedicated Fisher forecasting code~\citep{Borhanian:2020ypi} to within X percent.
This demonstrates that AD can be used to accurately produce population level forecasts.
